Appendix

### 2020-05-21 appendix_final.Rmd
add selection info

#### PACKAGES ####

# Needed packages
pkgs <- c('tidyverse', 'rvest', 'RSelenium')

@@

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. XXXX (Copiar da parte de métodos).

@@

We used XXXX

@@

### Binomial Tests for Coefficient Sigs

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n poses that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. The test consists in contrasting the number of occurences of positive and negative signs (Binomial trials) against the hypothesis that they were produced with 0.5 percent chance. Note that if this is the case, any detected difference would be a mere XXXX of chance.

@@

## Meta-analysis

@@

\newpage
## Meta-Analysis (all coefficients)

@@

## Meta-regressions

@@

@@

aux <- list(mod3, mod4, mod5, mod6, mod1, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_rows) %>%
    mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. < 0.10, ".", " ")))))
      )) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
  select(-`T`,-CI,-`P-Value`,-order) %>%
  pivot_longer(cols = c("Estimate", "SE")) %>%
  pivot_wider(names_from = model, values_from = c(value)) %>%
  select(-name)

@@

```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        "Base",
        "Full",
        "Base",
        "Full",
        "Base",
        "Full"
      )) %>% 
  collapse_rows(1:2,row_group_label_position ='identity',
                latex_hline = "none") %>%
  add_header_above(c(" ","ExpPC" = 2, "logExpPC" = 2, "PCTGDP" = 2)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header",
      "full_width"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

## Summary of Results (Permutation)

aux <- list(mod3_permu, mod4_permu, mod5_permu, mod6_permu, mod1_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_rows) %>%
    mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. < 0.10, ".", " ")))))
      )) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
  select(-`T`,-CI,-`P-Value`,-order) %>%
  pivot_longer(cols = c("Estimate", "SE")) %>%
  pivot_wider(names_from = model, values_from = c(value)) %>%
  select(-name)

```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        "Base",
        "Full",
        "Base",
        "Full",
        "Base",
        "Full"
      )) %>% 
  collapse_rows(1:2,row_group_label_position ='identity',
                latex_hline = "none") %>%
  add_header_above(c(" ","ExpPC" = 2, "logExpPC" = 2, "PCTGDP" = 2)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header",
      "full_width"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

@@

## Robustness: Full model meta-regressions combined

>>>>

#### INSTALLING PACKAGES ####

install.packages('tidyverse')
install.packages('rvest')
install.packages('RSelenium')

#### LOADING PACKAGES ####

library(tidyverse)
library(rvest)
library(RSelenium)

@@

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest.  Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.

In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set. Below is the data extraction process for all relevant coefficients in the selected articles. In the \@ref(meta-an) and \@ref(meta-reg) sections of this Appendix, you will find all tests performed in both reduced and full samples.

@@

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$). The additional moderators are: 1) electoral system; 2) data aggregation level; 3) estimation method; 4) publication year; 5) paper publication in an academic journal. The table below presents descriptive statistics for these moderators in our selection of articles.

@@

### Binomial Tests for Coefficient Signs

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n poses we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. The test consists in contrasting the number of occurences of positive and negative signs (Binomial trials) against the hypothesis that they were produced with 0.5 percent chance. Note that if this is the case, any detected difference would be a mere XXXX of chance.

@@

## Meta-analysis {#meta-an}

@@

\newpage
## Meta-Analysis (all coefficients) {#full-meta-an}

@@

## Meta-regressions {#meta-reg}

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World"))

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  filter(` ` != "Method: RDD") %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~(ifelse(is.na(.), " ", .)))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)

\blandscape

```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "Signif",
        #
        "Estimate",
        "SE",
        "Signif"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

```
\elandscape

@@

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  filter(` ` != "Method: RDD") %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. >= 0.05, " ", 
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)

@@

\blandscape
## Summary of Results (Permutation)
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "Signif",
        #
        "Estimate",
        "SE",
        "Signif",
        #
        "Estimate",
        "SE",
        "Signif"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

```
\elandscape

@@

## Robustness: Full model meta-regressions combined {#full-meta-reg}
